% CV link & https://github.com/anupadkh/Curriculum-Vitae/blob/master/anup_cv.pdf \\
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
% (c) 2008 Nathaniel Johnston <nathaniel@nathanieljohnston.com> http://www.nathanieljohnston.com
%
%This work is licensed under the Creative Commons Attribution-Noncommercial-Share Alike 2.5 License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/2.5/ or send a letter to Creative Commons, 543 Howard Street, 5th Floor, San Francisco, California, 94105, USA.



\documentclass[letterpaper,11pt]{article}
\newlength{\outerbordwidth}
\pagestyle{empty}
\raggedbottom
\raggedright
\usepackage[svgnames]{xcolor}
\usepackage{framed}
\usepackage{tocloft}
\usepackage{etoolbox}
\robustify\cftdotfill


%-----------------------------------------------------------
%Edit these values as you see fit

\setlength{\outerbordwidth}{3pt}  % Width of border outside of title bars
\definecolor{shadecolor}{gray}{0.75}  % Outer background color of title bars (0 = black, 1 = white)
\definecolor{shadecolorB}{gray}{0.93}  % Inner background color of title bars


%-----------------------------------------------------------
%Margin setup

\setlength{\evensidemargin}{-0.25in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\paperheight}{11in}
\setlength{\paperwidth}{8.5in}
\setlength{\tabcolsep}{0in}
\setlength{\textheight}{9.5in}
\setlength{\textwidth}{7in}
\setlength{\topmargin}{-0.3in}
\setlength{\topskip}{0in}
\setlength{\voffset}{0.1in}


%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{\vspace{8pt}
  \parbox{\textwidth}{\setlength{\FrameSep}{\outerbordwidth}
    \begin{shaded}
\setlength{\fboxsep}{0pt}\framebox[\textwidth][l]{\setlength{\fboxsep}{4pt}\fcolorbox{shadecolorB}{shadecolorB}{\textbf{\sffamily{\mbox{~}\makebox[6.762in][l]{\large #1} \vphantom{p\^{E}}}}}}
    \end{shaded}
  }\vspace{-5pt}
}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.5in}{l@{\cftdotfill{\cftsecdotsep}\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------


\begin{document}

\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
\textbf{\Large Anup Adhikari} & \textbf{\today} \\
Assistant Professor at Gandaki University & i@anup.pro.np \\
+977-9856070774 & http://www.anup.pro.np \\
% CV link & https://github.com/anupadkh/Curriculum-Vitae/blob/master/anup_cv.pdf \\
\end{tabular*}
\\

% \resheading{General Information}
% \begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
% Date of Birth & 2049-08-24 (BS) \\ & 1992-12-09 (AD) \\
% Marital Status & Unmarried \\
% Languages Spoken & Nepali, English, Hindi \\
% Profession & Engineer \\
% Nationality & Nepali \\
% Permanent Address & Machhapuchhre-6, Kaski (Dhital-8, Kaski) \\
% Current Address & Pokhara-8, Kaski \\

% \end{tabular*}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Work Experience}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}

\item[ ]
	\ressubheading{Gandaki University}{Pokhara, Nepal}{Assistant Professor}{2021 - present}
	\begin{itemize}
	  \resitem{Teaching Courses: Programming in C, Problem Solving and Logic}
	  
	  \resitem{Research Activities: Study of Education Management Information System of Gandaki Province for Development of Recommendation Engine}

	\end{itemize}

\item[ ]
	\ressubheading{Simle Infotech Private Limited}{Kathmandu, Nepal}{Co-founder}{2017 - 2021}
	\begin{itemize}
	  \resitem{Helping lead a world class team to eliminate expensive trial and error from every experts workflow. Using cutting edge optimization behind a simple API to help tune machine learning models and build better products in a variety of fields.}
	  
	  \resitem{Developed a Portal system of Kushma Municipality in Django-Python with MongoDB for storing all the household details and local government activities. Deployed in GIDC cloud architecture and enriched a national level software in E-Governance.}

	\end{itemize}

\item[] \ressubheading{Department of Electronics and Computer Engineering, IOE}{Lalitpur, Nepal}{Instructor}{2018}
	\begin{itemize}
		\resitem{Teaching Assistant}
		\resitem{\textit{Taught Subjects:} C-programming, Electromagnetics and Digital Signal Processing (6 months)}
	\end{itemize}

\item[] \ressubheading{Ubiquotous Based Learning -Research \& Development}{NSDeVil-Nepal, Lalitpur}{Senior Developer}{July 2018-July 2019}
	\begin{itemize}
		\resitem{Manage different project developments for Nepal.}
		\resitem{Coordinate with various team members and developers on software development inside the office.}
		\resitem{Developed NSD-Examination Result Processing System using openpyxl-python for Ubiquotous Based Examination System.}
		\resitem{Developed Language translator using openpyxl-python for preexisting codes}
		\resitem{Designed Learning Management System using Node.js and python}
	\end{itemize}

\item[] \ressubheading{Laboratory for ICT Research and Development}{Research Assistant}{IOE, Pulchowk}{2018}
	\begin{itemize}
		\resitem{Committee: Associate Prof. Sanjeeb Pandey PhD., Prof. Shashidhar Ram Joshi PhD., Baburam Dawadi, Dr. Aman Shakya}
		\resitem{Assist in research works of PhD. students.}
		\resitem{Develop system softwares for research labs in python}
		\resitem{Network Management and Examination Managements inside the ICTC premises.}
	\end{itemize}


\item[]
	\ressubheading{Office of District Development Committee Parbat}{Kushma, Parbat, Nepal}{ICT Engineer}{2014-2017}
	\begin{itemize}
		\resitem{{\bf IT Engineer:} \begin{itemize}
			\item Organized trainings in software based knowledge. Taught the local government officials on e-governance tools and softwares, accounting systems and other MIS systems. 
			\item Coordinate with Local Development Officer, District Engineer, Information Officer, Governance Expert and other Development Officers. 
			\item ICT Survey on requirement of IT infrastructure in various regions of Parbat district.
		\end{itemize} }
    \resitem{{\bf System Development:} Developed local infrastructure database system, online GIS web application for Bridge Network. Designed the LAN network architecture of Office of District Development Committee Parbat, now Office of District Coordination Committee Parbat.}
	\end{itemize}

	

\item[]
	\ressubheading{Everest Engineering College}{Lalitpur, Nepal}{Project Supervisor and Python Tutor}{July 2019 - Sept 2019}
	\begin{itemize}
			\resitem{{\bf Project Supervisor:} Co-developed and led team for RT-vehicle detection: Using Yolo, the team developed a real time vehicle detection system to count the no. of persons and vehicles moving in college streets.}
			
            \resitem{{\bf Python Tutor:} Taught the final year students about the hands-on knowledge in python programming.}
            % \resitem{{\bf Leadership:} Led cross-organization teams as director of the Yelp Dataset Challenge, MOE team lead, intern and new-hire mentor, founder and organizer of Applied Learning Group (bi-weekly, all-engineering technical speaker series) and more. Successfully managed projects from inception to on-time completion; balancing tradeoffs and coordinating teamwork.}
            % \resitem{{\bf Recruiting:} Created, implemented, and directed \texttt{yelp.com/dataset\_challenge}, gave many dozens of tech talks across the country, led events, gave hundreds of technical interviews, and closed candidates.}
	\end{itemize}


\end{itemize}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Academic Qualification}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}

\item

	\ressubheading{Tribhuwan University, Institute of Engineering, Pulchowk Campus}{Lalitpur, Nepal}{M.Sc. in Computer Science and Knowledge Engineering}{2017-2020}

	\begin{itemize}
		\resitem{Graduated in First Division with Distinction}
		\resitem{Department of Electronics and Computer Engineering (Full Scholarship)}
		\resitem{Thesis - Prediction of Protein Drug Interaction from their Sequence: Using SMILES and FASTA, Coordinator: Dr. Aman Shakya, Supervisor: Associate Prof. Dr. Surendra Shrestha}
		\resitem{{\bf Majors:} Computer System, Cloud Computing, Knowledge Engineering, Image Processing, Operation Research, Algorithmic Mathematics, Big Data, Object Oriented Database Management System, Machine Learning, Semantic Web Technology }
	\end{itemize}

\item

	\ressubheading{Paschimanchal Campus}{Pokhara, Kaski}{Bachelors in Electronics and Communication Engineering}{2009 - 2013}

	\begin{itemize}

		\resitem{Graduated in First Division} 
		
		\resitem{Majors in Database System, Aeronautical Communication and Remote Sensing}

		\resitem{Major subjects: Digital Signal Processing, Electronic Devices, Computer System Architecture, C++ Programming, Digital Logic}
		\resitem{Strong emphasis on programming, numerical analysis and embedded system Designs}

		\resitem{Minor Project in LED Array Display using 8051 Microcontroller}

		\resitem{Major Project in Voice Controlled Home Automation using Arduino}
		

	\end{itemize}

\item \ressubheading{Sagarmatha Higher Secondary School}{Nayabazar, Pokhara, Nepal}{+2 Science}{2007-2009}
	\begin{itemize}
		\resitem{Major in Mathematics}
	\end{itemize}

\item \ressubheading{SOS Hermann Gmeiner School Gandaki}{Rambazar, Pokhara, Nepal}{Upto 10 (SLC)}{2000-2007}
\begin{itemize}
	\resitem{Majors in Computer Science}
\end{itemize}

\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Research Experience}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
\item
	\ressubheading{Laboratory for ICT Research and Development, IOE}{Pulchowk, Lalitpur, Nepal}{Research Assistant  under Er. Baburam Dawadi}{2018 October to July 2019}
	\begin{itemize}
		\resitem{Transformations to Future Networking with Broadband and IoT Implementations \texttt{(TraFNet)}}
	\resitem{Study the current trend of networking technologies migrations including broadband deployment and the IoT implementation for future smart life}
	\resitem{Find the position of Nepal regarding Broadband deployment, SDN/IPv6 migration \& IoT implementation.}
	\resitem{Analyze the future network transformation challenges and recommend the solution for Nepal}
	\end{itemize}
\item 
	\ressubheading{Prediction of Protein Drug Interaction from Sequence}{Thesis - IOE, Nepal}{With Devi Basnet Phd., Senior Research Scientist, South Korea}{November 2018 - November 2019}
	\begin{itemize}
		\resitem{Wrote \textbf{open source} machine learning tool in \texttt{python} for protein sequence and drug sequence analysis. The FASTA model of protein and SMILES model of drug were analysed for predicting their behaviour. Other feature representations were employed to build a proper feature matrix for prediction.}
    \resitem{Used ConvNet models to discover sequence alignments and predict a preferable drug-protein set.}
	\end{itemize}
\item
	\ressubheading{DataGenerator for DNCON2}{UMSL, USA}{Assistant Programmer under Badri Adhikari duing CASP event}{2017-2018}
	\begin{itemize}
		\resitem{Developed a DataGenerator for machine learning experiment of protein fold prediction DNCON2 during the famous CASP competition.}
	\end{itemize}
% \item
% 	\ressubheading{Max Plank Institute for the Physics of Complex Systems}{Dresden, Germany}{NSF REU Research Assistant under Prof. Steven Tomsovic}{Summer 2007}
% 	\begin{itemize}
% 		\resitem{Research on extreme value statistics in \texttt{MATLAB} and \texttt{FORTRAN}}
% 	\end{itemize}
% \item
% 	\ressubheading{University of California: Davis}{Davis, CA}{NSF REU Research Assistant under Prof. Daniel Cox}{Summer 2006}
% 	\begin{itemize}
% 		\resitem{Computational biophysics research as applied to protein folding in \texttt{Java}}
% 	\end{itemize}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Publications}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{enumerate}
 \item Anup Adhikari, {\it PREDICTION OF PROTEIN DRUG INTERACTION FROM THEIR SEQUENCE: USING SMILES AND FASTA}. Masters Thesis in Computer Science and Knowledge Engineering, Tribhuwan University, November 2019.
 \item Anup Adhikari, Anish Karki, Bigyan Pandit, and Prabin Shrestha {\it Speech Operated System for Home Appliances} {\it B.Eng. Major Project} 
 \item Editorial Board {\it ENSCITECH magazine} 
\end{enumerate}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Skills}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}

\item {\bf Numerical Analysis and Computer Science:} Machine Learning, Data Mining, Optimization, Computational Science, Artificial Intelligence, Linear Algebra, ODEs, PDEs, Iterative Methods

\item {\bf Public Speaking:} I've given presentations during my tenure in DDC-Parbat to the general public audience.

\item {\bf Development:} Python (preferred), C/C++, Java, HTML, JavaScript, \LaTeX

\item {\bf Technology:} Numerical libraries, Web frameworks, databases, Linux, git, vim, tmux

\item Diverse background in Math, Computer Science, Physics and Biology allows me to communicate to a wide scientific and general audience and begin contributing to any group immediately.

\end{itemize}

\resheading{Awards}
\vspace{-2pt}
	\begin{center}\begin{tabular*}{6.6in}{l@{\extracolsep{\fill}}r}
		\multicolumn{2}{c}{Under-Graduate Scholarship Award (NRs. 160,000) \cftdotfill{\cftdotsep}2010}\\
		\multicolumn{2}{c}{Graduate Scholarship Award (NRs.100,000) \cftdotfill{\cftdotsep}2017} \\
		\multicolumn{2}{c}{Best Local Development Software Award for Kushma Portal System \cftdotfill{\cftdotsep}2018 }
	\end{tabular*}
\end{center}

% \begin{itemize}[label={}]
% 	\item {Best Local Development Software Award. Awarded by}
	
% \end{itemize}

\resheading{References}
\begin{tabular*}{7in}{l@{\extracolsep{\fill}}c}
	Associate Professor Sanjeeb Prasad Panday PhD. & Director \\
	& Information and Communication Center, IOE \\
	& Tribhuwan University \\
	& sanjeeb@ioe.edu.np \\
	& +977 9840052621 \\
	% \toprule
	\\ \\
	Associate Professor Surendra Shrestha PhD. & Head of Department \\
	& Department of Electronics and Computer Engineering, IOE \\
	& Tribhuwan University \\
	& surendra@ioe.edu.np \\
	& +977 9851198713 \\
	\\ \\
	Mr. Shiva Prasad Rijal & Local Development Officer \\
	& Office of District Development Committee Parbat \\
	& shivarijal1972@gmail.com \\
	& +977-9857630430 \\
	
\end{tabular*}

\end{document}

