
    
    % \resheading{General Information}
    % \begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
    % Date of Birth & 2049-08-24 (BS) \\ & 1992-12-09 (AD) \\
    % Marital Status & Unmarried \\
    % Languages Spoken & Nepali, English, Hindi \\
    % Profession & Engineer \\
    % Nationality & Nepali \\
    % Permanent Address & Machhapuchhre-6, Kaski (Dhital-8, Kaski) \\
    % Current Address & Pokhara-8, Kaski \\
    
    % \end{tabular*}
    
    
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \resheading{Work Experience}
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \begin{itemize}
    
        % \item[] 
        % \ressubheading{Maharudra Group Private Limited}{Kathmandu, Nepal}{Team Leader}{2019 - Present}
        % \begin{itemize}
        % 	\resitem{Conduct cyber-attack simulations as part of the RED team activity}
        % 	\resitem{Conduct Vulnerability Assessment and Penetration Testing and configuration review for network, web application , mobile application and thick -client application}
        % 	\resitem{Conduct configuration reviews for OS , DB, Firewall, routers, Switches and other security devices/components}
        % 	\resitem{Perform manual testing of web applications}
        % 	\resitem{Conduct source-code review using automated and manual approaches}
        % 	\resitem{Prepare detailed reports}
        % 	\resitem{Ensure timely delivery of status updates and final reports to clients}
        % 	\resitem{Handle Clients queries}
        % \end{itemize}
    
    \item[ ]
        \ressubheading{Simle Infotech Private Limited}{Kathmandu, Nepal}{Senior Developer}{2017 - Present}
        \begin{itemize}
          \resitem{Helping lead a world class team to eliminate expensive trial and error from every experts workflow. Using cutting edge optimization behind a simple API to help tune machine learning models and build better products in a variety of fields.}
          
          \resitem{Developed a Portal system of Kushma Municipality in Django-Python with MongoDB for storing all the household details and local government activities. Deployed in GIDC cloud architecture and enriched a national level software in E-Governance.}

          \resitem{Developed \textbf{Data Portal System for Gandaki Province Policy and Planning Commission} based on Angular and Python - Django Rest Framework.}

          \resitem{Developed different result processing modules for schools and colleges in \textbf{Samagyan} based on ODOO ERP.}

          \resitem{Developed accounting application interface for Tripathi Foam Industries based on ODOO ERP.}

        \end{itemize}
    
    \item[] \ressubheading{Department of Electronics and Computer Engineering, IOE}{Lalitpur, Nepal}{Instructor}{2018}
        \begin{itemize}
            \resitem{Teaching Assistant}
            \resitem{\textit{Taught Subjects:} C-programming, Electromagnetics and Digital Signal Processing (6 months)}
        \end{itemize}
    
    \item[] \ressubheading{Ubiquotous Based Learning -Research \& Development}{NSDeVil-Nepal, Lalitpur}{Senior Developer}{July 2018-July 2019}
        \begin{itemize}
            \resitem{Manage different project developments for Nepal.}
            \resitem{Coordinate with various team members and developers on software development inside the office.}
            \resitem{Developed NSD-Examination Result Processing System using openpyxl-python for Ubiquotous Based Examination System.}
            \resitem{Developed Language translator using openpyxl-python for preexisting codes}
            \resitem{Designed Learning Management System using Node.js and python}
        \end{itemize}
    
    \item[] \ressubheading{Laboratory for ICT Research and Development}{Research Assistant}{IOE, Pulchowk}{2018}
        \begin{itemize}
            \resitem{Committee: Associate Prof. Sanjeeb Pandey PhD., Prof. Shashidhar Ram Joshi PhD., Baburam Dawadi, Dr. Aman Shakya}
            \resitem{Assist in research works of PhD. students.}
            \resitem{Develop system softwares for research labs in python}
            \resitem{Network Management and Examination Managements inside the ICTC premises.}
        \end{itemize}
    
    
    \item[]
        \ressubheading{Office of District Development Committee Parbat}{Kushma, Parbat, Nepal}{ICT Engineer}{2014-2017}
        \begin{itemize}
            \resitem{{\bf IT Engineer:} \begin{itemize}
                \item Organized trainings in software based knowledge. Taught the local government officials on e-governance tools and softwares, accounting systems and other MIS systems. 
                \item Coordinate with Local Development Officer, District Engineer, Information Officer, Governance Expert and other Development Officers. 
                \item ICT Survey on requirement of IT infrastructure in various regions of Parbat district.
            \end{itemize} }
        \resitem{{\bf System Development:} Developed local infrastructure database system, online GIS web application for Bridge Network. Designed the LAN network architecture of Office of District Development Committee Parbat, now Office of District Coordination Committee Parbat.}
        \end{itemize}
    
        
    
    \item[]
        \ressubheading{Everest Engineering College}{Lalitpur, Nepal}{Project Supervisor and Python Tutor}{July 2019 - Sept 2019}
        \begin{itemize}
                \resitem{{\bf Project Supervisor:} Co-developed and led team for RT-vehicle detection: Using Yolo, the team developed a real time vehicle detection system to count the no. of persons and vehicles moving in college streets.}
                
                \resitem{{\bf Python Tutor:} Taught the final year students about the hands-on knowledge in python programming.}
                % \resitem{{\bf Leadership:} Led cross-organization teams as director of the Yelp Dataset Challenge, MOE team lead, intern and new-hire mentor, founder and organizer of Applied Learning Group (bi-weekly, all-engineering technical speaker series) and more. Successfully managed projects from inception to on-time completion; balancing tradeoffs and coordinating teamwork.}
                % \resitem{{\bf Recruiting:} Created, implemented, and directed \texttt{yelp.com/dataset\_challenge}, gave many dozens of tech talks across the country, led events, gave hundreds of technical interviews, and closed candidates.}
        \end{itemize}
    
    
    \end{itemize}